\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-08-30 paper/manuscript.tex
improved caption for figure 6

%US map
\begin{figure}[htp]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\includegraphics[width=\linewidth]{figures/us_map.pdf} \vspace{-2cm}
		\caption{Cities in the corpus, by partisanship of mayor.}
	\label{us_map}
\end{figure}

>>>>

%US map
\begin{figure}[htp]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\includegraphics[width=\linewidth]{figures/us_map.pdf} \vspace{-2cm}
		\caption{Map of the cities in the corpus in the contiguous U.S. The corpus also includes Alaska. In the analysis, only cities in California, Indiana, Louisiana, New York, Texas and Washington are used. The colors represent the partisanship of the mayor (blue corresponding to Democrats and red to Republicans).}
	\label{us_map}
\end{figure}
